Team size and composition in home health care

### 2023-10-26 paper-presentation/paper-presentation.qmd
Minor

## Principle 4: Team composition
::: r-fit-text
$$
min \sum\limits_{k∈Q} w_kC_k\\
s.t. C_k + e_k ≥ μ_k + η_ασ_k, ∀k ∈ Q,\\
C_k ∈ {0}∪[l,∞), ∀k ∈ Q,\\
$$
Where:

- $Q = \{1,2,...,K\}, K ∈ N$, is a set of qualification levels with an ordering such that capacity of QL $k$ can be deployed to cover demand of all QLs $j≤k$ as well.

- $N_k$ is the required demand for QL $k∈Q$ in a given week and $N_k$ is normally distributed with mean $μ_k$ and variance $σ_k^2$.
- $C_k ≥ 0$ is the capacity of QL $k$ deployed over the given week.

- Each unit of capacity of QL $k$ comes at a cost $w_k ≥ 0$, with $w_j ≤ w_k$, if $j ≤ k$.

- Due to the minimum size of contracts, if capacity of QL $k$ is used (i.e., $C_k > 0$), then the corresponding capacity should at least be $l$ units.
:::

>>>>

## Principle 4: Team composition
::: r-fit-text

$$
min \sum\limits_{k∈Q} w_kC_k\\
s.t. C_k + e_k ≥ μ_k + η_ασ_k, ∀k ∈ Q,\\
C_k ∈ {0}∪[l,∞), ∀k ∈ Q,\\
$$
:::
